---
title: "Coursera Developing Data Products: Course Project
"
author: "Hassan"
date: "August 16, 2018"
output:
  slidy_presentation: null
  ioslides_presentation: default
---

##'Introduction'

This presentation is created as part of the requirement for the Coursera Developing Data Products Course. Objectives of the assignment are to understanding the essential concepts such as :

- shiny to build data product application and reactive output .  

- R-Presentation or slidify to create data product related presentations .

##'The Application'

An application based on the "salary" dataset from [R] has been developed and deployed at : https://hbarar.shinyapps.io/Salaries/ . The app allows to perform interactive data analysis from a set of user specified criterias . Therfore User will be able to further refine the results by choosing the influential parameters as below:

- Gender
- Rank
- Years since getting PhD
- Years of experience range 

The source codes for ui.R and server.R files are also available on the GitHub repo

##"Data"

Below is a brief look at the data which consists of the 
salary coloumn categorized by 4 factors :

```{r}

data <- read.csv("Salary.csv", sep=",", header=T)
head(data[2:7],4)


 

```
Question : What would be the estimation salary for persons who : 
    
- Are male
- Professors
- years since PhD : 5 years
- service : 15 to 20 years

-Note: Through shiny app you can change the above settings and 
      as a result , the table, histogram and output would coordinate and
      change subsequently

##Result
```{r}

 library(png)
img<-readPNG('C:\\Users\\hassan\\Desktop\\Data-Product -Project\\Salaries\\image.png')
 grid::grid.raster(img)
```


